\Large{Learning to Pivot with Adversarial Networks}

### 2016-10-31 tex/paper.tex
save

As previously discussed, the proposed solution can be used in any situation
where the training data may not be representative of the real data the
predictive model will be applied to in practice. In the scientific context, this
includes situations where the data generation processes are associated to
systematic uncertainties (e.g., as in high energy physics), and which would be
certainly interesting to revisit in light of the proposed solution. More generally,
the approach also extends to cases where independence of the predictive
model with respect to random variables is desired, as in domain adaptation
or fairness in classification.

>>>>

As previously discussed, the proposed solution can be used in any situation
where the training data may not be representative of the real data the
predictive model will be applied to in practice. In the scientific context, this
includes situations where the data generation processes are associated to
systematic uncertainties (e.g., as in high energy physics), and which would certainly be
 interesting to revisit in light of the proposed solution. More generally,
the approach also extends to cases where independence of the predictive
model with respect to random variables is desired, as in domain adaptation
or fairness in classification. Again, trying our algorithm on these
use cases is certaintly worth investigating.
